A holomorphic approach to membranes and fivebranes

### 2022-06-29 fivebranes/fact.tex
merge

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

@@

\end{document}

>>>>

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

@@

We summarize the key points of this section.
In both the fivebrane and membrane case, we have described a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables restricted to the worldvolume of the fivebrane or membrane.
This factorization algebra is of the form 
\[
\pi_*\Obs_{sugra} = \clie^\bu(\cG)
\]
where $\cG$ is a sheaf of $L_\infty$ algebras on the worldvolume of the fivebrane or membrane.
While $\infty$ rank, $\cG$ is still well-behaved geometrically. 
It is given as the sheaf of sections of a pro vector bundle.

This local $L_\infty$ algebra came with a natural decomposition 
\[
\cG = \oplus_{j \geq -1} \cG^{(j)} .
\]
The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
This sequence of ideals induces a limit diagram of vector bundles
\beqn\label{eqn:lim}
0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
\eeqn
where $0$ is the zero vector bundle.
For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
For $N > 0$, we define 
\beqn
\til \cG_N \define \cG / \cG^{(\geq N-1)} 
\eeqn
which has the induced structure of a local $L_\infty$ algebra on the worldvolume.

The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
\beqn\label{eqn:colim}
\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\cG_2) \to \cdots ,
\eeqn
whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
There is a similar diagram upon applying~$!$-duals
\beqn
\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots ,
\eeqn 
whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$.

%\end{document}

### 2022-06-29 fivebranes/index.tex
merge

@@

Generally speaking, twists of supersymmetric theories have a mixed holomorphic and topological behavior.

@@

%In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
%We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
%We recount how it acts on the vector space \eqref{eqn:localfree}.
% 
%Recall that the even part of $E(3|6)$ consists of two summands:
%\[
%\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
%\]
%Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
%An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.

After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
This algebra contains the $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

To compute characters of local operators the fivebrane worldvolume theory we will consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
\beqn\label{eqn:bosonic1}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\eeqn
We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.

For convenience we choose coordinates on the eleven manifold as
\[
\C^5 \times \R = \C_z^3 \times \C_w^2 \times \R_t
\]
with $z_i, i=1,2,3$ and $w_a, a=1,2$.
The stack of fivebranes wrap $w_1=w_2=t=0$. 
Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.

\begin{itemize}
\item
The subalgebra $\lie{sl}(3)$ embeds as vector fields
\[
\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
\]
\item
The subalgebra $\lie{gl}(1)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
\] 
Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
\item 
The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
\]
\end{itemize}

The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
We choose these explicitly as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
  \beqn
  z_1 \del_{z_1} - z_2 \del_{z_2} , \quad z_2 \del_{z_2} - z_3 \del_{z_3}
  \eeqn
  on~$\C^{3}_{z}$.
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_+,r_-\}$. 
  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
  \hline
  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
\end{tabular}
\caption{Fugacities for a single fivebrane.}
\end{center}
\label{tbl:weights1}
\end{table}

\subsection{Operators on a single fivebrane}

We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
This theory exists on any complex three-fold $X$. 
To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.

The theory on a single fivebrane is free and the underlying cochain complex of the abelian holomorphic local Lie algebra on $\C^3$ is given by 
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

\begin{lem}
\label{lem:single}
The $\Z \times \Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
\Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
\eeqn
\end{lem}

\begin{proof}
The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
On the formal disk all closed two-forms are automatically exact, which implies the lemma.
\end{proof}

We now move on to the computation of the character of local operators on a single fivebrane.
According to the weights listed above and using the description of local operators in Lemma \label{lem:single} we have the following contributions to the character.

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

Putting this all together we obtain the following.

\begin{prop}
The character of local operators of the holomorphic twist of the theory on a single fivebrane is given by the following plethystic exponential
\[
{\rm PExp} \left[f_{tensor} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{prop}

A degeneration of this character was computed in \cite{KR1}. 
They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
\[
\frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3}
\]
which agrees with our direct analysis above.

There are various specializations of this character that one can consider. 
One which is motivated from supersymmetry produces...

\begin{itemize}
\item The deformation $\d z_1 \otimes r_+$.
\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
\end{itemize}

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.

>>>>

After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

In this section we will compute characters of the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes.
Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
We will enumerate states via considering a Cartan in the even subalgebra
\beqn\label{eqn:bosonic1}
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\eeqn
%We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.

For convenience we choose coordinates on the eleven manifold as
\[
\R \times \C^5 = \R_t \times \C^2_w \times \C_z^3 
\]
with $z = (z_i), i=1,2,3$ and $w = (w_a), a=1,2$.
The stack of fivebranes wrap $w_1=w_2=t=0$. 
Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.

\begin{itemize}
\item
The subalgebra $\lie{sl}(3)$ embeds as vector fields
\beqn
\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
\eeqn
By definition, these vector fields are automatically divergence-free.
\item
The generator of the subalgebra $\lie{gl}(1)$ is mapped to the element
\beqn\label{eqn:Y}
Y = \sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
\eeqn 
Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $t=w=0$. 
\item 
The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
\beqn
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
\eeqn
\end{itemize}

The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
We choose these explicitly as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
  \beqn
  h_1 = z_1 \del_{z_1} - z_2 \del_{z_2} , \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3}.
  \eeqn
   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element~$\eqref{eqn:Y}$. 
  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
  \beqn
  h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
  \eeqn
\end{itemize}
The weights are summarized in table \ref{tbl:weights1}.
Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.

%\begin{table}
%\begin{center}
%\begin{tabular}{c c c c c c}
%  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
%  \hline
%  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
%  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
%  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
%  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
%\end{tabular}
%\caption{Fugacities for a single fivebrane.}
%\end{center}
%\label{tbl:weights1}
%\end{table}

\subsection{Global symmetry for twisted membranes}

@@

We enumerate single particle supergravity states via computing the super trace of the operator $t_1^{h_1} t_2^{h_2} q^Y r^h$. 
The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.

@@
